### 2016-06-17 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream report, new flow meter picture
Updated acknowledgements section of hose stream report

\headerC{
\flushright{
Joseph M. Willi \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
September 2015}}

@@

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

% ==========================
% = RESULTS AND DISCUSSION =
% ==========================

\chapter{Results and Discussion}
\label{chap:results}
In the following sections, the measurements are presented in graphic and tabular form. In the graphs, an error bar will represent the estimated uncertainty of the measurement. In the tables, the uncertainty will be included in the caption of the table as a percentage enclosed in brackets.

@@

The authors would like to thank Roy McLane, Kristopher Overholt, Keith Stakes, Nicholas Dow, and Jay MCElroy from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.

>>>>

\headerC{
\flushright{
Joseph M. Willi \\
Daniel Madrzykowski$^*$ \\
Craig G. Weinschenk$^+$ \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
June 2016}

\vspace*{2\baselineskip}
\textit{$^*$\small Currently with UL FSRI}
\\
\textit{$^+$\small Currently with JENSEN HUGHES}
}

@@

\begin{figure}[!ht]
	\includegraphics[width=3in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

% ==========================
% = RESULTS AND DISCUSSION =
% ==========================
\chapter{Results and Discussion}
\label{chap:results}
In the following sections, the measurements are presented in graphic and tabular form. In the graphs, an error bar will represent the estimated uncertainty of the measurement. In the tables, the uncertainty will be included in the caption of the table as a percentage enclosed in brackets.

@@

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.
